---
title: "final project work"
author: "Tyler Park (tmpark3)"
date: "12/09/2020"
output: html_document
---

```{r}
#install.packages("mltools")
library(mltools)
library(data.table)
```


**Loading data set in R from the CSV file, and converting **
```{r}
car_data = read.csv("Cars_data.csv")
car_data = subset(car_data, select = -c(Vehicle.Style, Market.Category))
#unique(car_data$Transmission.Type)
#colnames(car_data)
#unique(car_data$Engine.Fuel.Type)
#unique(car_data$Driven_Wheels)
unique(car_data$Vehicle.Size)
#head(car_data)
```


**Removing the dew non automatic/manual transmission types, and storing this new data in car_data_transd data frame**
```{r}
car_data_transd<-car_data[!(car_data$Transmission.Type=="AUTOMATED_MANUAL" | car_data$Transmission.Type=="DIRECT_DRIVE" | car_data$Transmission.Type=="UNKNOWN"),]
unique(car_data_transd$Transmission.Type)
```


**Removing certain fuel types, keeping only gasoline and diesel. Storing the result in car_data_fuel data frame**

```{r}
car_data_fuel<-car_data_transd[!(grepl("flex", car_data_transd$Engine.Fuel.Type, fixed = TRUE)
|car_data_transd$Engine.Fuel.Type=="electric" | car_data_transd$Engine.Fuel.Type=="" | car_data_transd$Engine.Fuel.Type=="natural gas"),]
unique(car_data_fuel$Engine.Fuel.Type)
```


**Assigning the different types of gasoline to a single "gasoline value". Now, the only two values for fuel type will be "gasoline" and "diesel" as visible below**

```{r}
car_data_fuel$Engine.Fuel.Type[car_data_fuel$Engine.Fuel.Type == "premium unleaded (required)" ] <- "gasoline"
car_data_fuel$Engine.Fuel.Type[car_data_fuel$Engine.Fuel.Type == "regular unleaded" ] <- "gasoline"
car_data_fuel$Engine.Fuel.Type[car_data_fuel$Engine.Fuel.Type == "premium unleaded (recommended)" ] <- "gasoline"
unique(car_data_fuel$Engine.Fuel.Type)
```


**One hot encoding - converting categorical variables to values which R will understand**
```{r}
car_data_factored = car_data_fuel
car_data_factored$Vehicle.Size <- factor(car_data_factored$Vehicle.Size)
car_data_factored$Transmission.Type <- factor(car_data_factored$Transmission.Type)
car_data_factored$Engine.Fuel.Type <- factor(car_data_factored$Engine.Fuel.Type)
car_data_factored$Driven_Wheels <- factor(car_data_factored$Driven_Wheels)
levels(car_data_factored$Vehicle.Size)
levels(car_data_factored$Transmission.Type)
levels(car_data_factored$Engine.Fuel.Type)
levels(car_data_factored$Driven_Wheels)
car_data_factored = one_hot(as.data.table(car_data_factored))
```


**Added a variable to dataset (ReleasedYearsAgo) which stores the value of the years ago this model was released**

```{r}
car_data_factored$ReleasedYearsAgo <- with(car_data_factored, 2020 - Year)
head(car_data_factored)
```



**Modeling**

```{r}
#install.packages("dplyr")
#install.packages("ggplots2")
#install.packages("caret")
library(dplyr)
library(ggplot2)
library(caret)

set.seed(100)
#train-test  split using 65% of the data
samplesize = round(0.65*nrow(car_data_factored), 0)
index = sample(seq_len(nrow(car_data_factored)), size = samplesize)

data_train = car_data_factored[index,]
data_test = car_data_factored[-index,]

msrp_mod = lm(MSRP ~., data_train)
#summary(msrp_mod)

msrp_mod2 = lm(MSRP ~ highway.MPG + Make + Popularity, data_test)
#summary(msrp_mod2)

#anova(msrp_mod2, msrp_mod)
```


**Assumptions**

```{r}
#linearity
resact = data.frame(residual = msrp_mod$residuals, fitted = msrp_mod$fitted.values)

resact %>% ggplot(aes(fitted, residual)) + geom_point() + geom_smooth() + geom_hline(aes(yintercept = 0)) + 
    theme(panel.grid = element_blank(), panel.background = element_blank())

#normality test
shapiro.test(msrp_mod$residuals)

#multicollinearity
vif = vif(msrp_mod)
max(vif)
```


**Making model improvements**

```{r}

```


